Guarded Recursion in Agda via Sized Types

### 2019-01-28 code-oneclock-paper/latex/paper.tex
working on Sec 4

\newcommand{\GTT}{\textbf{GTT}}

@@

Next we define categorical semantics for the syntax defined in \Cref{sec:syntax}.
To do so, we use a similar method as used by M{\o}gelberg \cite{Mogelberg14}.
The interpretation of types depend on the clock contexts.
If the clock context is empty, then types become sets.
If the clock context has one clock, then types are interpreted as objects in the topos of trees.

@@

\subsection{Modelling Simple Types}
%\label{sec:kripke}
\input{CloTT/Structure/Contexts}

\input{CloTT/Structure/Types}

\input{CloTT/Structure/Terms}

\input{CloTT/Structure/Subst}

\input{CloTT/Structure/DefinitionalEquality}

\input{CloTT/Structure/ContextOperations}

>>>>

\newcommand{\GTT}{\textbf{GTT}}
\newcommand{\Set}{\mathbf{Set}}

@@

Next we give a categorical semantics for the calculus introduced in
\Cref{sec:syntax}.  We take inspiration from M{\o}gelberg's model
\cite{Mogelberg14}, where a (simple) type in a clock context
containing $n$ clocks is interpreted
as a presheaf in $\Set^{(\omega^n)^{\text{op}}}$, where $\omega$ is
the preorder of ordered natural numbers. In our model we replace the
category $\omega$ with the preorder of sizes. Moreover we only
consider the cases where either the clock context is empty or it
contains exactly one clock. This means that a type in \GTT\ is either
interpreted as an element of \F{Set} or as a presheaf over \F{Size}. 
In this section we show how to implement presheaves and how to model
the fragment of \GTT\ corresponding to simply typed lambda
calculus. The interpretation of the guarded recursive and coinductive
features of \GTT\ is given in Section \ref{sec:guarded}.
%% interpreted a $n = 0$ or $n = 1$. where Since in \GTT\
%% every 
%% consider clock contexts containing at most one clock.
%% The type
%% \AD{ClockCtx}  of syntactic clock contexts is also used for semantic clock contexts.
%% 
%% 
%% 
%% a variation of the topos of
%% trees, where as the indexing category we replace the category of
%% ordered natural numbers with the preorder of sizes.
%% 
%% he similar to To do so, we use a similar method as used by M{\o}gelberg \cite{Mogelberg14}.
%% The interpretation of types depend on the clock contexts.
%% If the clock context is empty, then types become sets.
%% If the clock context has one clock, then types are interpreted as objects in the topos of trees.

@@

\subsection{Modelling Simple Types}
%\label{sec:kripke}
\input{CloTT/Structure/Contexts}
\input{CloTT/Structure/Types}
\input{CloTT/Structure/Terms}
\input{CloTT/Structure/Subst}
\input{CloTT/Structure/DefinitionalEquality}
\input{CloTT/Structure/ContextOperations}
